---
title: "Week 2 Assignment: Power Machines Representatives"
author: "ABRAMOV Andrey"
date: "October 4, 2016"
output: html_document
---

## Course name
Developing Data Products by Johns Hopkins University

## Goal of the Assignment
1) Create a web page using R Markdown that features a map created with Leaflet. 
Webpage must contain the date of creating the document, and it must contain a map created with Leaflet.
2) Host your webpage on either GitHub Pages, RPubs, or NeoCities.

## Coding

```{r}
library(leaflet)
# collectin the data
# real adress could be found at www.power-m.ru
PM_offices <- data.frame(lat = c(59.961836, 55.78074, 54.54242, 47.236947, 56.338499),
                         lng = c(30.38184, 37.639374, 36.270881, 38.900358, 30.536467),
                         popup = c("Head Office", "Moscow Office", "Kalufa workshop", "Krasny kotelchik workshop", "Reostat workshop"))
PM_offices <- as.data.frame(PM_offices)
# prepare a PM icon for the map
PM_icon <- makeIcon(iconUrl="http://www.metaprom.ru/foto_news/1351234343foto1_big.jpg", 
                    iconWidth=50*600/450, iconHeight=50*450/600)
# correcting the data type
PM_offices$lat <- as.numeric(as.character(PM_offices$lat))
PM_offices$lng <- as.numeric(as.character(PM_offices$lng))
PM_offices$popup <- as.character(PM_offices$popup)

```

So the map with markers looks like the next:

```{r, echo=FALSE}
PM_map <- leaflet() %>%  addTiles() %>% addMarkers(lat=PM_offices$lat, lng=PM_offices$lng, popup=PM_offices$popup, icon=PM_icon)
PM_map
```

Thank you for your attention!
Andrey ABRAMOV

